Partridge: An effective system for the automatic classification of the types of academic papers

### 2013-05-25 doc/bcspaper/article.tex
Expanded PloS rather than reporting url twice
Updated James' email address to ravenscroft@papro.org.uk

\title*{Partridge: An effective system for the automatic classification of the types of academic papers}
\titlerunning{Partridge: classifying academic papers}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
%\author{James Ravenscroft\,$^{1}$\footnote{to whom correspondence should be addressed}, Maria Liakata\,$^{2,3}$ and Amanda Clare$^{1}$}
%\address{$^{1}$Department of Computer Science, Aberystwyth University,
%$^{2}$Department of Computer Science, University of Warwick,
%$^{2}$Text mining group, EMBL-EBI Cambridge}
\author{James Ravenscroft \and Maria Liakata \and Amanda Clare}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{James Ravenscroft, Amanda Clare \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK  \email{jrr9@aber.ac.uk}
\and Maria Liakata \at Department of Computer Science, University of Warwick \email{M.Liakata@warwick.ac.uk}}

@@

\subsection*{Collection of scientific articles} Partridge allows users to
upload any paper which is free of copyright restrictions.  For the purpose of
this study we needed a large set of papers that we could label with CoreSC to
investigate how this information assists classification into paper type.  Open
Access (OA) journals provide free read access to their papers, but many do not
permit the user of articles for data mining purposes. The PLoS
journals\footnote{PLoS: \url{http://www.plos.org/}} contain large volumes of OA
literature under a permissive license that allows data mining.  They also use
the PubMed Central markup schema, which is compatible with SAPIENTA, for papers
published through their journal. The PLoS journals advanced search offers
approximately 50 types of paper through which to restrict the search.  Many of
these paper type categories contain too few papers to be useful, others are too
specific (e.g. {\it Message from PLoS}) or appear rather {\it ad hoc}. Indeed it is not
clear how these paper types have been identified. We chose to look at a range
of types, some of which we expect to overlap or have an unclear distinction.
These are namely: Essay, Correspondence, Case Study, Perspective,
Viewpoint, Opinion, Review, Research.

>>>>

\title*{Partridge: An effective system for the automatic classification of the types of academic papers}
\titlerunning{Partridge: classifying academic papers}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
%\author{James Ravenscroft\,$^{1}$\footnote{to whom correspondence should be addressed}, Maria Liakata\,$^{2,3}$ and Amanda Clare$^{1}$}
%\address{$^{1}$Department of Computer Science, Aberystwyth University,
%$^{2}$Department of Computer Science, University of Warwick,
%$^{2}$Text mining group, EMBL-EBI Cambridge}
\author{James Ravenscroft \and Maria Liakata \and Amanda Clare}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{James Ravenscroft, Amanda Clare \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK  \email{ravenscroft@papro.org.uk}, \email{afc@aber.ac.uk}
\and Maria Liakata \at Department of Computer Science, University of Warwick \email{M.Liakata@warwick.ac.uk}}

@@

\subsection*{Collection of scientific articles} Partridge allows users to
upload any paper which is free of copyright restrictions.  For the purpose of
this study we needed a large set of papers that we could label with CoreSC to
investigate how this information assists classification into paper type.  Open
Access (OA) journals provide free read access to their papers, but many do not
permit the user of articles for data mining purposes. The Public Library of
Science (PLoS) journals contain large volumes of OA literature under a
permissive license that allows data mining.  They also use the PubMed Central
markup schema, which is compatible with SAPIENTA, for papers published through
their journal. The PLoS journals advanced search offers approximately 50 types
of paper through which to restrict the search.  Many of these paper type
categories contain too few papers to be useful, others are too specific (e.g.
{\it Message from PLoS}) or appear rather {\it ad hoc}. Indeed it is not clear
how these paper types have been identified. We chose to look at a range of
types, some of which we expect to overlap or have an unclear distinction.
These are namely: Essay, Correspondence, Case Study, Perspective, Viewpoint,
Opinion, Review, Research.
